Negative Types

### 2015-03-22 Univalence/outline.tex
renaming

\paragraph*{TypeEquivalences.} Establishes that the Agda types $\bot$, $\top$, $\uplus$, and $\times$ form a commutative semiring using $\simeq$ as the underlying equivalence relation.

\paragraph*{FinEquiv.} Establishes that $\texttt{Fin}~n$ also forms a commutative semiring with $\simeq$ as the underlying equivalence relation. In particular, we have:
\[\begin{array}{rcll}
\texttt{Fin}~0 &\simeq& \bot \\
\texttt{Fin}~1 &\simeq& \top \\
\texttt{Fin}~(m+n) &\simeq& \texttt{Fin}~m \uplus \texttt{Fin}~n \\
\texttt{Fin}~(m*n) &\simeq& \texttt{Fin}~m \times \texttt{Fin}~n
\end{array}\]
and then we have all the commutative semiring axioms, e.g., $\texttt{Fin}~(0+m) \simeq \texttt{Fin}~m$. \textbf{SOME AXIOMS MISSING: TO COMPLETE ???}

>>>>

\paragraph*{TypeEquiv.} Establishes that the Agda types $\bot$, $\top$, $\uplus$, and $\times$ form a commutative semiring using $\simeq$ as the underlying equivalence relation.

\paragraph*{FinEquiv.} Establishes that $\texttt{Fin}~n$ also forms a commutative semiring with $\simeq$ as the underlying equivalence relation. In particular, we have:
\[\begin{array}{rcll}
\texttt{Fin}~0 &\simeq& \bot \\
\texttt{Fin}~1 &\simeq& \top \\
\texttt{Fin}~(m+n) &\simeq& \texttt{Fin}~m \uplus \texttt{Fin}~n \\
\texttt{Fin}~(m*n) &\simeq& \texttt{Fin}~m \times \texttt{Fin}~n
\end{array}\]
and then we have all the commutative semiring axioms, e.g.,
$\texttt{Fin}~(0+m) \simeq \texttt{Fin}~m$.

\paragraph*{CauchyEquiv.}
